Community-Conditioned Language Models

### 2021-05-03 paper/plot_macros.tex
updates to paper

>>>>

% https://tex.stackexchange.com/questions/183778/how-can-several-boxplots-be-combined-into-a-single-figure-as-groups/183856#183856
\newcommand{\pplbycommbox}{
  \begin{axis}
    \addplot+[boxplot={draw position=-0.2, box extend=0.2}, draw=blue] table [y=lstm-3-0_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=0.2, box extend=0.2}, draw=red] table [y=transformer-3-0_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=.8, box extend=0.2}, draw=blue] table [y=lstm-3-1_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=1.2, box extend=0.2}, draw=red] table [y=transformer-3-1_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=1.8, box extend=0.2}, draw=blue] table [y=lstm-3-2_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=2.2, box extend=0.2}, draw=red] table [y=transformer-3-2_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=2.8, box extend=0.2}, draw=blue] table [y=lstm-3-3_ig] {floats/ig_by_comm.csv};
    \addplot+[boxplot={draw position=3.2, box extend=0.2}, draw=red] table [y=transformer-3-3_ig] {floats/ig_by_comm.csv};
  \end{axis}
}
